\section{Some Useful Tricks for Using Transition Matrix}
Oberve that, in the next step, we must in some state in the MC. 
\begin{proposition}[Normality]
  \[
    \sum_{y\in\Omega} P(x, y) = 1,\hspace{0.5cm} \forall x\in\Omega
  \]
\end{proposition}
Then, consider the multiplication between the transition matrix and some functino $f:\Omega \to \mathbb{R}$.
\begin{define}[Left Multiplication]
  \[[fP](y) = \sum_{x\in\Omega}f(x)P(x,y)\]
\end{define}
What's the meaning of the left multiplication?
\begin{proposition}[It Generates A New Distribution]
If $f$ is some distribution, then $fP$ forms a new distribution $f'$. 
\tcblower
Moreover, this could be easily generalized to the $t$-step case. That is, $fP^t$ is a new distribution.
\end{proposition}
\begin{proof}
  \begin{align*}
    \sum_{y\in\Omega} [fP](y)
    &= \sum_{y\in\Omega}\sum_{x\in\Omega} f(x)P(x,y)\\
    &= \sum_{x\in\Omega}f(x)\sum_{y\in\Omega}P(x,y) \\
    &= \sum_{x\in\Omega}f(x) \\
    &= 1 \qedhere
  \end{align*}
\end{proof}
Actually this new distribution $f'(x)$ means the probability that select a state $x_0$ in the distribution of $f$, move according to the markov chain, and finally end in state $x$.

\begin{define}[Right Multiplication]
  \[[Pf](x) = \sum_{y\in\Omega}P(x,y)f(y)\]
\end{define}
And, what's the meaning of the right multiplication?
\begin{proposition}[It Could Represent The Probability of move from state $x$ to Some Fixed State Set]
  Here, $f$ is no longer a distribution. Suppose here is a state set $A\in\Omega$. Then, we could construct $f$ as a indicator of $A$:
  \[
    f(x) = \left\{
      \begin{array}{l}
        1, \hspace{0.5cm} \mbox{if $x\in A$} \\
        0, \hspace{0.5cm} \mbox{otherwise}
      \end{array}
    \right.
  \]
  Then we have:
  \[
    [Pf](x) = \sum_{y\in A}P(x,y) = P(x, A)
  \]
  \tcblower
  Note that this could be generalized to $t$-step case easily. That is
  \[
    [P^tf](x) = P^t(x,A)
  \]
\end{proposition}
Note that $||P^t(x,\cdot) - \pi||_{TV}$ is closely related to the mixing time of the markov chain.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../../notebook"
%%% End:
